The Hot Hand Fallacy in Call of Duty

### 2022-08-23 paper/paper.Rmd
spaces between + and -, other writing clean up

```{r}
#| label: setup-code
library(dplyr)
library(tidyr)
library(purrr)
library(gt)
library(scales)

@@

1.  Both have economic aspects that can create clear advantages for one team in a round, given how prior rounds played out. CoD has no such equivalent, except for perhaps "kill streaks", which infrequently occur.
2.  Teams play either offense or defense for many consecutive rounds. (The former has a 15-15-1 format and the latter uses a 12-12-1 format.) On the other hand, teams in CoD SnD rotate roles every round, analogous to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series for professional sports like the MLB, NBA, and NHL.[^14] While theoretically one might be able to account for any kind of format, such as a 5-5-1, the rotation of team sides every round is convenient for convincing ourselves that rounds could reasonably be modeled as i.i.d. Bernoulli trials.
3.  Both Counter-Strike and Valorant have overtime rules---team must win by two rounds---which can make end-of-series sequences difficult to model. CoD SnD does not have overtime rules.

@@

Stepping back from the one-sided perspective of a single team's round win probability when streaking, one can attempt to detect the hot hand phenomenon with a Wald-Wolfowitz runs test. Under the null hypothesis, the number of runs in a sequence of $r$ trials, $\zeta(r)$, is a random variable that can take on values $r^+$ and $r^-$ for success and failure respectively, with the following mean $\mu$ and variance $\sigma^2$.

```{=tex}
\begin{equation}\label{eq:ww}
\mu = \frac{2r^{+}r^{-}}{r} + 1, \sigma^2 = \frac{(\mu-1)(\mu-2)}{r-1}
\end{equation}
```
To incorporate our findings regarding constant round win probability, We can specify that $\Pr(r^+) = \phi$ (and, conversely, that $\Pr(r^-) = 1 - \phi$).

One can subset the observed series sequences to those that violate the null hypothesis for the run test and perform a test of equal proportions, where the null is that the observed rate of a sequence, $\psi$, is equal to the expected rate of the sequence, $\hat{psi}$. The test statistic is

```{=tex}
\begin{equation}\label{eq:prop}
Z = \frac{\hat{\psi} - \psi}{\sqrt{\psi_d (1 - \psi_d) ( \frac{1}{\hat{N}} + \frac{1}{N})}}
\end{equation}
```
where $N$ is the observed number of sequences, $\hat{N}$ is the expected number, and $\psi_d = \frac{\psi - \hat{psi}}{N - \hat{N}}$. If we can reject the null hypothesis for such sequences, then there is implicit evidence in favor of the hot hand.

@@

First, we investigate the constant probability assumption and the distribution of rounds played in a series. Chance's [-@chance2020] work is closely related to our, and, in fact, provides a guide for this investigation. Afterwards, We investigate post-streak win rates, referring to work from MS. We finish with a brief look at sequences of round wins violating the Wald-Wolfowitz runs test, and whether such observed sequences occur more frequently than expected.

@@

```{r}
#| label: cod_round_win_prop_after_k_wins_i_rounds-table

cod_round_win_prop_after_k_wins_i_rounds |> 
  mutate(
    across(notional_p_value, p.adjust)
  ) |>
  filter(
    win_round,
    # round >= (n_rounds - 3)
    n_rounds >= 10,
    win_streak == 3
  ) |>  
  filter(total >= 10) |> 
  mutate(
    across(
      matches('p_value'), 
      ~case_when(
        .x <= 0.01 ~ '<=0.01', 
        TRUE ~ sprintf('%.2f', .x)
      )
    ),
    prop_lab = scales::percent(prop, accuracy = 0.1),
    notional_lab = scales::percent(notional_prop, accuracy = 0.1)
  ) |>
  arrange(n_rounds, round, win_series, win_round) |> 
  transmute(
    n_rounds,
    round,
    across(win_series, ~ifelse(.x, 'yes', 'no')),
    n,
    total,
    prop_lab,
    notional_lab
  ) |> 
  gt::gt() |> 
  gt::cols_label(
    n_rounds = 'r',
    round = 'i',
    win_series = 'Win series?',
    n = 'r+',
    total = 'N',
    prop_lab = 'O',
    notional_lab = 'a'
  ) |> 
  gt::as_latex() |> 
  cat()

@@

cod_expected_round_arrangements_mle <- simulate_cod_round_arrangements(0.575)

@@

cod_round_arrangements_mle <- cod_expected_round_arrangements_mle |> perform_run_tests()
cod_round_arrangements_mle |> 
  filter(is_significant) |> 
  filter(n_rounds < 11) |> 
  transmute(
    n_rounds,
    ws,
    n_actual,
    across(prop_actual, ~sprintf('%.2f%%', 100 * .x)),
    across(n_expected_adj, round, 2),
    across(prop_expected, ~sprintf('%.2f%%', 100 * .x))
  ) |> 
  gt::gt() |> 
  gt::cols_label(
    n_rounds = 'r',
    ws = 'Sequence',
    n_actual = 'a',
    prop_actual = 'b',
    n_expected_adj = 'c',
    prop_expected = 'd'
  ) |> 
  gt::as_latex() |> 
  cat()
```

@@

\caption{Sequences ($\zeta(r)$) for which we can reject Wald-Wolfowitz null hypothesis for $r \in [8, 9, 10]$, where round wins $r^+$ and losses $r^-$ are denoted by $+$ and $-$ respectively. The observed count, $N^{\zeta r}$, and proportion, $P^{\zeta r}$, of all possible sequences, as well as the expected count, $\hat{N}^{\zeta r}$, and proportion, $\hat{P}^{\zeta r}$. $\hat{N}^{\zeta r}$ is scaled to the observed number of series played, hence its non-integer value.}
\label{tbl:cod-runs} \\

\toprule
r & $\zeta(r)$ & $N^{\zeta r}$ & $P^{\zeta r}$ & $\hat{N}^{\zeta r}$ & $\hat{P}^{\zeta r}$ \\ 
\midrule
8 & --++++++ & 4 & 0.47\% & 7.67 & 0.90\% \\ 
9 & ---++++++ & 4 & 0.47\% & 3.75 & 0.44\% \\ 
10 & ++++----++ & 1 & 0.12\% & 2.39 & 0.28\% \\ 
10 & +----+++++ & 0 & 0.00\% & 2.04 & 0.24\% \\ 
10 & +-+-++-+-+ & 3 & 0.35\% & 2.04 & 0.24\% \\ 
10 & +++----+++ & 2 & 0.23\% & 2.04 & 0.24\% \\ 
10 & ----++++++ & 2 & 0.23\% & 1.79 & 0.21\% \\ 
10 & +-+-+-++-+ & 3 & 0.35\% & 1.70 & 0.20\% \\ 
10 & +-++-+-+-+ & 0 & 0.00\% & 1.70 & 0.20\% \\ 
10 & ++----++++ & 1 & 0.12\% & 1.19 & 0.14\% \\ 
10 & +-+-+-+-++ & 3 & 0.35\% & 1.11 & 0.13\% \\ 
10 & ++-+-+-+-+ & 0 & 0.00\% & 1.11 & 0.13\% \\ 
10 & +++++----+ & 2 & 0.23\% & 1.02 & 0.12\% \\ 
\bottomrule
\end{longtable}
```
The relative frequency of the expected proportions are based on 10,000 simulations using the constant round probability $\phi_2 = 0.575$. A test for the difference between the observed and expected proportions of all sequences, $P^{\zeta r}$ and $\hat{P}^{\zeta r}$ respectively, indicates that the null hypothesis---that the two proportions are equal---cannot be rejected for any of the 25 significant sequences.

@@

In the future, we could have account for prior team strengths, both in general and on specific maps. Even if doing so does not change the results, we could gain additional insight into why we do not observe statistically significant streakiness.

Further regarding future work, we've reached out to the Twitter user "R11stats", who privately tracks in-round player engagements.[^26] R11stats expressed intent on making the data public, which would allow for research into player-specific momentum.

@@

Other talking points

-

>>>>

```{r}
#| label: setup-code
library(readr)
library(dplyr)
library(tidyr)
library(purrr)
library(gt)
library(scales)

@@

1.  Both have economic aspects that can create clear advantages for one team in a round, given how prior rounds played out. CoD has no such equivalent, except for perhaps "score streaks", which infrequently occur.
2.  Teams play either offense or defense for many consecutive rounds. (The former has a 15-15-1 format and the latter uses a 12-12-1 format.) On the other hand, teams in CoD SnD rotate roles every round, analogous to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series for professional sports like the MLB, NBA, and NHL.[^14] While theoretically one might be able to account for any kind of format, such as a 5-5-1, the rotation of team sides every round is convenient for convincing ourselves that rounds could reasonably be modeled as i.i.d. Bernoulli trials.
3.  Both Counter-Strike and Valorant have overtime rules---team must win by two rounds---which can make end-of-series sequences difficult to model. CoD SnD does not have overtime rules.

@@

Stepping back from the one-sided perspective of a single team's round win probability when streaking, one can attempt to detect the hot hand phenomenon with a Wald-Wolfowitz runs test. Under the null hypothesis, the number of runs in a sequence of $r$ trials, $\zeta(r)$, is a random variable that can take on values $r^+$ and $r^- = r - r^+$ for the number of success and failure respectively, with the following mean $\mu$ and variance $\sigma^2$:

```{=tex}
\begin{equation}\label{eq:ww}
\mu = \frac{2r^{+}r^{-}}{r} + 1, \sigma^2 = \frac{(\mu-1)(\mu-2)}{r-1}.
\end{equation}
```
To incorporate our findings regarding constant round win probability, We can specify that $\Pr(r^+) = \phi$ (and, conversely, that $\Pr(r^-) = 1 - \phi$).

One can subset the observed series sequences to those that violate the null hypothesis for the run test and perform a test of equal proportions, where the null is that the observed proportion of a sequence relative to all possible sequences, $P(\zeta) = P^\zeta$, is equal to the expected proportion of the sequence relative to all possible sequences, $\hat{P}^\zeta$. The test statistic is

```{=tex}
\begin{equation}\label{eq:prop}
Z = \frac{P^\zeta - \hat{P}^\zeta}{\sqrt{P^\zeta_{\delta} (1 - P^\zeta_{\delta}) (1 / N^\zeta + 1 / \hat{N}^\zeta)  } }
\end{equation}
```
where

$$
P^\zeta_{\delta} = \frac{P^\zeta - \hat{P}^\zeta}{N^\zeta - \hat{N}^\zeta}
$$

and where $N^\zeta$ is the observed number of sequences, $\hat{N}^\zeta$ is the expected number of sequences. If we can reject the null hypothesis for such sequences, then there is implicit evidence in favor of the hot hand.

@@

First, we investigate the constant probability assumption and the distribution of rounds played in a series. Chance's work is closely related to our, and, in fact, provides a guide for this investigation. Afterwards, We investigate post-streak win rates, referring to work from MS. We finish with a brief look at sequences of round wins violating the Wald-Wolfowitz runs test, and whether such observed sequences occur more frequently than expected.

@@

```{r}
#| label: cod_round_win_prop_after_k_wins_i_rounds-table
cod_round_win_prop_after_k_wins_i_rounds |> 
  mutate(
    across(notional_p_value, p.adjust)
  ) |>
  filter(
    win_round,
    # round >= (n_rounds - 3)
    n_rounds >= 10,
    win_streak == 3
  ) |>  
  filter(total >= 10) |> 
  mutate(
    across(
      matches('p_value'), 
      ~case_when(
        .x <= 0.01 ~ '<=0.01', 
        TRUE ~ sprintf('%.2f', .x)
      )
    ),
    prop_lab = scales::percent(prop, accuracy = 0.1),
    notional_lab = scales::percent(notional_prop, accuracy = 0.1)
  ) |>
  arrange(n_rounds, round, win_series, win_round) |> 
  transmute(
    n_rounds,
    round,
    across(win_series, ~ifelse(.x, 'yes', 'no')),
    n,
    total,
    prop_lab,
    notional_lab
  ) |> 
  gt::gt() |> 
  gt::cols_label(
    n_rounds = 'r',
    round = 'i',
    win_series = 'Win series?',
    n = 'r+',
    total = 'N',
    prop_lab = 'O',
    notional_lab = 'a'
  ) |> 
  gt::as_latex() |> 
  cat()

@@

cod_expected_round_arrangements_naive <- simulate_cod_round_arrangements(0.5)
cod_expected_round_arrangements_mle <- simulate_cod_round_arrangements(0.575)

@@

cod_round_arrangements_naive <- cod_expected_round_arrangements_naive |> perform_run_tests()
cod_round_arrangements_mle <- cod_expected_round_arrangements_mle |> perform_run_tests()

cod_round_arrangements_mle |> 
  filter(is_significant) |> 
  filter(n_rounds < 11) |> 
  transmute(
    n_rounds,
    ws,
    n_actual,
    across(prop_actual, ~sprintf('%.2f%%', 100 * .x)),
    across(n_expected_adj, round, 2),
    across(prop_expected, ~sprintf('%.2f%%', 100 * .x))
  ) |> 
  gt::gt() |> 
  gt::cols_label(
    n_rounds = 'r',
    ws = 'Sequence',
    n_actual = 'a',
    prop_actual = 'b',
    n_expected_adj = 'c',
    prop_expected = 'd'
  ) |> 
  gt::as_latex() |> 
  cat()
```

@@

\caption{Sequences ($\zeta(r)$) for which we can reject Wald-Wolfowitz null hypothesis for $r \in [8, 9, 10]$, where round wins and losses are denoted with $+$ and $-$ respectively. The observed count, $N^{\zeta r}$, and proportion, $P^{\zeta r}$, of all possible sequences, as well as the expected count, $\hat{N}^{\zeta r}$, and proportion, $\hat{P}^{\zeta r}$. $\hat{N}^{\zeta r}$ is scaled to the observed number of series played, hence its non-integer value.}
\label{tbl:cod-runs} \\

\toprule
r & $\zeta(r)$ & $N^{\zeta r}$ & $P^{\zeta r}$ & $\hat{N}^{\zeta r}$ & $\hat{P}^{\zeta r}$ \\ 
\midrule
8 & - - + + + + + + & 4 & 0.47\% & 7.67 & 0.90\% \\ 
9 & - - - + + + + + + & 4 & 0.47\% & 3.75 & 0.44\% \\ 
10 & + + + + - - - - + + & 1 & 0.12\% & 2.39 & 0.28\% \\ 
10 & + - - - - + + + + + & 0 & 0.00\% & 2.04 & 0.24\% \\ 
10 & + - + - + + - + - + & 3 & 0.35\% & 2.04 & 0.24\% \\ 
10 & + + + - - - - + + + & 2 & 0.23\% & 2.04 & 0.24\% \\ 
10 & - - - - + + + + + + & 2 & 0.23\% & 1.79 & 0.21\% \\ 
10 & + - + - + - + + - + & 3 & 0.35\% & 1.70 & 0.20\% \\ 
10 & + - + + - + - + - + & 0 & 0.00\% & 1.70 & 0.20\% \\ 
10 & + + - - - - + + + + & 1 & 0.12\% & 1.19 & 0.14\% \\ 
10 & + - + - + - + - + + & 3 & 0.35\% & 1.11 & 0.13\% \\ 
10 & + + - + - + - + - + & 0 & 0.00\% & 1.11 & 0.13\% \\ 
10 & + + + + + - - - - + & 2 & 0.23\% & 1.02 & 0.12\% \\ 
\bottomrule
\end{longtable}
```
The relative frequency of the expected proportions are based on 10,000 simulations using the constant round probability $\phi_2 = 0.575$. A test for the difference between the observed and expected proportions of all sequences, $P^{\zeta r}$ and $\hat{P}^{\zeta r}$ respectively, indicates that the null hypothesis---that the two proportions are equal---cannot be rejected for any of the 25 significant sequences.

@@

In the future, we could account for the quality of the teams, both in general and on specific maps. Even if doing so does not change the results, we could gain additional insight into why we do not observe statistically significant streakiness.

Further regarding future work, we have contacted the Twitter user "R11stats", who privately tracks in-round player engagements.[^26] R11stats expressed intent on making the data public, which would allow for research into player-specific momentum. While it seems there is no team-level hot hand effect in CoD SnD, perhaps there is with eliminations performed by individual players.

@@

### 2022-08-23 paper/paper.tex
spaces between + and -, other writing clean up

Stepping back from the one-sided perspective of a single team's round
win probability when streaking, one can attempt to detect the hot hand
phenomenon with a Wald-Wolfowitz runs test. Under the null hypothesis,
the number of runs in a sequence of \(r\) trials, \(\zeta(r)\), is a
random variable that can take on values \(r^+\) and \(r^-\) for success
and failure respectively, with the following mean \(\mu\) and variance
\(\sigma^2\).

\begin{equation}\label{eq:ww}
\mu = \frac{2r^{+}r^{-}}{r} + 1, \sigma^2 = \frac{(\mu-1)(\mu-2)}{r-1}
\end{equation}

@@

One can subset the observed series sequences to those that violate the
null hypothesis for the run test and perform a test of equal
proportions, where the null is that the observed rate of a sequence,
\(\psi\), is equal to the expected rate of the sequence, \(\hat{psi}\).
The test statistic is

\begin{equation}\label{eq:prop}
Z = \frac{\hat{\psi} - \psi}{\sqrt{\psi_d (1 - \psi_d) ( \frac{1}{\hat{N}} + \frac{1}{N})}}
\end{equation}

where \(N\) is the observed number of sequences, \(\hat{N}\) is the
expected number, and \(\psi_d = \frac{\psi - \hat{psi}}{N - \hat{N}}\).
If we can reject the null hypothesis for such sequences, then there is
implicit evidence in favor of the hot hand.

@@

First, we investigate the constant probability assumption and the
distribution of rounds played in a series. Chance's (2020) work is
closely related to our, and, in fact, provides a guide for this
investigation. Afterwards, We investigate post-streak win rates,
referring to work from MS. We finish with a brief look at sequences of
round wins violating the Wald-Wolfowitz runs test, and whether such
observed sequences occur more frequently than expected.

@@

\caption{Sequences ($\zeta(r)$) for which we can reject Wald-Wolfowitz null hypothesis for $r \in [8, 9, 10]$, where round wins $r^+$ and losses $r^-$ are denoted by $+$ and $-$ respectively. The observed count, $N^{\zeta r}$, and proportion, $P^{\zeta r}$, of all possible sequences, as well as the expected count, $\hat{N}^{\zeta r}$, and proportion, $\hat{P}^{\zeta r}$. $\hat{N}^{\zeta r}$ is scaled to the observed number of series played, hence its non-integer value.}
\label{tbl:cod-runs} \\

\toprule
r & $\zeta(r)$ & $N^{\zeta r}$ & $P^{\zeta r}$ & $\hat{N}^{\zeta r}$ & $\hat{P}^{\zeta r}$ \\ 
\midrule
8 & --++++++ & 4 & 0.47\% & 7.67 & 0.90\% \\ 
9 & ---++++++ & 4 & 0.47\% & 3.75 & 0.44\% \\ 
10 & ++++----++ & 1 & 0.12\% & 2.39 & 0.28\% \\ 
10 & +----+++++ & 0 & 0.00\% & 2.04 & 0.24\% \\ 
10 & +-+-++-+-+ & 3 & 0.35\% & 2.04 & 0.24\% \\ 
10 & +++----+++ & 2 & 0.23\% & 2.04 & 0.24\% \\ 
10 & ----++++++ & 2 & 0.23\% & 1.79 & 0.21\% \\ 
10 & +-+-+-++-+ & 3 & 0.35\% & 1.70 & 0.20\% \\ 
10 & +-++-+-+-+ & 0 & 0.00\% & 1.70 & 0.20\% \\ 
10 & ++----++++ & 1 & 0.12\% & 1.19 & 0.14\% \\ 
10 & +-+-+-+-++ & 3 & 0.35\% & 1.11 & 0.13\% \\ 
10 & ++-+-+-+-+ & 0 & 0.00\% & 1.11 & 0.13\% \\ 
10 & +++++----+ & 2 & 0.23\% & 1.02 & 0.12\% \\ 
\bottomrule
\end{longtable}

@@

In the future, we could have account for prior team strengths, both in
general and on specific maps. Even if doing so does not change the
results, we could gain additional insight into why we do not observe
statistically significant streakiness.

Further regarding future work, we've reached out to the Twitter user
``R11stats'', who privately tracks in-round player
engagements.\footnote{\url{https://twitter.com/R11stats}} R11stats
expressed intent on making the data public, which would allow for
research into player-specific momentum.

Other talking points

\begin{itemize}
\tightlist
\item
\end{itemize}

>>>>

Stepping back from the one-sided perspective of a single team's round
win probability when streaking, one can attempt to detect the hot hand
phenomenon with a Wald-Wolfowitz runs test. Under the null hypothesis,
the number of runs in a sequence of \(r\) trials, \(\zeta(r)\), is a
random variable that can take on values \(r^+\) and \(r^- = r - r^+\)
for the number of success and failure respectively, with the following
mean \(\mu\) and variance \(\sigma^2\):

\begin{equation}\label{eq:ww}
\mu = \frac{2r^{+}r^{-}}{r} + 1, \sigma^2 = \frac{(\mu-1)(\mu-2)}{r-1}.
\end{equation}

@@

One can subset the observed series sequences to those that violate the
null hypothesis for the run test and perform a test of equal
proportions, where the null is that the observed proportion of a
sequence relative to all possible sequences, \(P(\zeta) = P^\zeta\), is
equal to the expected proportion of the sequence relative to all
possible sequences, \(\hat{P}^\zeta\). The test statistic is

\begin{equation}\label{eq:prop}
Z = \frac{P^\zeta - \hat{P}^\zeta}{\sqrt{P^\zeta_{\delta} (1 - P^\zeta_{\delta}) (1 / N^\zeta + 1 / \hat{N}^\zeta)  } }
\end{equation}

where

\[
P^\zeta_{\delta} = \frac{P^\zeta - \hat{P}^\zeta}{N^\zeta - \hat{N}^\zeta}
\]

and where \(N^\zeta\) is the observed number of sequences,
\(\hat{N}^\zeta\) is the expected number of sequences. If we can reject
the null hypothesis for such sequences, then there is implicit evidence
in favor of the hot hand.

@@

First, we investigate the constant probability assumption and the
distribution of rounds played in a series. Chance's work is closely
related to our, and, in fact, provides a guide for this investigation.
Afterwards, We investigate post-streak win rates, referring to work from
MS. We finish with a brief look at sequences of round wins violating the
Wald-Wolfowitz runs test, and whether such observed sequences occur more
frequently than expected.

@@

\caption{Sequences ($\zeta(r)$) for which we can reject Wald-Wolfowitz null hypothesis for $r \in [8, 9, 10]$, where round wins and losses are denoted with $+$ and $-$ respectively. The observed count, $N^{\zeta r}$, and proportion, $P^{\zeta r}$, of all possible sequences, as well as the expected count, $\hat{N}^{\zeta r}$, and proportion, $\hat{P}^{\zeta r}$. $\hat{N}^{\zeta r}$ is scaled to the observed number of series played, hence its non-integer value.}
\label{tbl:cod-runs} \\

\toprule
r & $\zeta(r)$ & $N^{\zeta r}$ & $P^{\zeta r}$ & $\hat{N}^{\zeta r}$ & $\hat{P}^{\zeta r}$ \\ 
\midrule
8 & - - + + + + + + & 4 & 0.47\% & 7.67 & 0.90\% \\ 
9 & - - - + + + + + + & 4 & 0.47\% & 3.75 & 0.44\% \\ 
10 & + + + + - - - - + + & 1 & 0.12\% & 2.39 & 0.28\% \\ 
10 & + - - - - + + + + + & 0 & 0.00\% & 2.04 & 0.24\% \\ 
10 & + - + - + + - + - + & 3 & 0.35\% & 2.04 & 0.24\% \\ 
10 & + + + - - - - + + + & 2 & 0.23\% & 2.04 & 0.24\% \\ 
10 & - - - - + + + + + + & 2 & 0.23\% & 1.79 & 0.21\% \\ 
10 & + - + - + - + + - + & 3 & 0.35\% & 1.70 & 0.20\% \\ 
10 & + - + + - + - + - + & 0 & 0.00\% & 1.70 & 0.20\% \\ 
10 & + + - - - - + + + + & 1 & 0.12\% & 1.19 & 0.14\% \\ 
10 & + - + - + - + - + + & 3 & 0.35\% & 1.11 & 0.13\% \\ 
10 & + + - + - + - + - + & 0 & 0.00\% & 1.11 & 0.13\% \\ 
10 & + + + + + - - - - + & 2 & 0.23\% & 1.02 & 0.12\% \\ 
\bottomrule
\end{longtable}

@@

In the future, we could account for the quality of the teams, both in
general and on specific maps. Even if doing so does not change the
results, we could gain additional insight into why we do not observe
statistically significant streakiness.

Further regarding future work, we have contacted the Twitter user
``R11stats'', who privately tracks in-round player
engagements.\footnote{\url{https://twitter.com/R11stats}} R11stats
expressed intent on making the data public, which would allow for
research into player-specific momentum.
